SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-02-22 scipy-1.0/paper.tex
different scale -> larger scale
He also shares should be past tense

As STScI continued to use Python for an increasingly large portion
of the Hubble Space Telescope data analysis pipeline, they encountered
problems with the Python numerical array container.
Numeric, the original array package, was
suitable for small arrays, but not for the large images processed by
STScI.  With the Numeric maintainer's blessing, the decision was made
to write NumArray, a library that could handle data on a different
scale.  Unfortunately, NumArray proved inefficient for small arrays,
presenting the community with a rather unfortunate choice.  In 2005,
Travis Oliphant combined the best elements of Numeric and NumArray,
thereby solving the dilemma and paving the way for Python to become
a very significant player in the Data Science movement. NumPy
1.0 was released in October 2006\cite{numpy-1.0-tag}, with about 30
authors recognized for major contributions in its release notes.

@@

%In April 2006, Paul
%Dubois\footnote{https://mail.python.org/pipermail/numpy-discussion/2006-April/007487.html} wrote
%to the NumPy mailing list:
%\begin{quote}
%IEEE's magazine, Computing in Science and Engineering (CiSE), has asked me
%to put together a theme issue on the use of Python in Science and
%Engineering. I will write an overview to be accompanied by 3-5 articles [. . .]
%that show a diverse set of applications or
%tools, to give our readers a sense of whether or not Pyth%on might be useful
%in their own work.
%\end{quote}
In a May/June 2007 special issue of IEEE Computing in Science and
Engineering, Paul Dubois wrote\cite{dubois2007guest}:
\begin{quote}
LLNL now has many Python-based efforts built from scratch or wrapped around
legacy codes [. . .] hundreds of thousands
of lines of C++, Python, and Fortran 95, all working together just as we hoped,
doing compute-intensive calculations on massively parallel computers.
\end{quote}
While it is now more commonly accepted, Dubois took the time to explain to
the 2007 reader that ``interpreted doesn't mean slow or only interactive.''
He also shares his own interest in Python for ``computational steering''
where ``Python serves as the input language to a scientific application, and the actual
computations are performed both in Python itself and in compiled extensions.''
%https://www.computer.org/csdl/mags/cs/2007/03/c3007.html
Using Python for computational steering was one of the earliest uses of Python
in large scientific processing pipelines.
In addition to Dubois' overview there were also articles introducing
Python and SciPy \cite{oliphant2007python}, IPython \cite{perez2007ipython},
and  Matplotlib \cite{hunter2007matplotlib}.
There was also a diverse set of
research applications including
systems biology\cite{myers2007python},
astronomy\cite{greenfield2007reaching},
robotics\cite{krauss2007python},
nanophotonics\cite{bienstman2007python},
partial differential equations\cite{mardal2007using},
neuroimaging\cite{millman2007analysis},
geographic information systems\cite{shi2007python}, and
education\cite{backer2007computational, myers2007pythona}.

>>>>

As STScI continued to use Python for an increasingly large portion
of the Hubble Space Telescope data analysis pipeline, they encountered
problems with the Python numerical array container.
Numeric, the original array package, was
suitable for small arrays, but not for the large images processed by
STScI.  With the Numeric maintainer's blessing, the decision was made
to write NumArray, a library that could handle data on a larger
scale.  Unfortunately, NumArray proved inefficient for small arrays,
presenting the community with a rather unfortunate choice.  In 2005,
Travis Oliphant combined the best elements of Numeric and NumArray,
thereby solving the dilemma and paving the way for Python to become
a very significant player in the Data Science movement. NumPy
1.0 was released in October 2006\cite{numpy-1.0-tag}, with about 30
authors recognized for major contributions in its release notes.

@@

%In April 2006, Paul
%Dubois\footnote{https://mail.python.org/pipermail/numpy-discussion/2006-April/007487.html} wrote
%to the NumPy mailing list:
%\begin{quote}
%IEEE's magazine, Computing in Science and Engineering (CiSE), has asked me
%to put together a theme issue on the use of Python in Science and
%Engineering. I will write an overview to be accompanied by 3-5 articles [. . .]
%that show a diverse set of applications or
%tools, to give our readers a sense of whether or not Pyth%on might be useful
%in their own work.
%\end{quote}
In a May/June 2007 special issue of IEEE Computing in Science and
Engineering, Paul Dubois wrote\cite{dubois2007guest}:
\begin{quote}
LLNL now has many Python-based efforts built from scratch or wrapped around
legacy codes [. . .] hundreds of thousands
of lines of C++, Python, and Fortran 95, all working together just as we hoped,
doing compute-intensive calculations on massively parallel computers.
\end{quote}
While it is now more commonly accepted, Dubois took the time to explain to
the 2007 reader that ``interpreted doesn't mean slow or only interactive.''
He also shared his own interest in Python for ``computational steering''
where ``Python serves as the input language to a scientific application, and the actual
computations are performed both in Python itself and in compiled extensions.''
%https://www.computer.org/csdl/mags/cs/2007/03/c3007.html
Using Python for computational steering was one of the earliest uses of Python
in large scientific processing pipelines.
In addition to Dubois' overview there were also articles introducing
Python and SciPy \cite{oliphant2007python}, IPython \cite{perez2007ipython},
and  Matplotlib \cite{hunter2007matplotlib}.
There was also a diverse set of
research applications including
systems biology\cite{myers2007python},
astronomy\cite{greenfield2007reaching},
robotics\cite{krauss2007python},
nanophotonics\cite{bienstman2007python},
partial differential equations\cite{mardal2007using},
neuroimaging\cite{millman2007analysis},
geographic information systems\cite{shi2007python}, and
education\cite{backer2007computational, myers2007pythona}.
